### 2023-08-22 paper/FPF-WG1.tex
sect 2
Update FPF-WG1.tex
sect 3
app A
new abstract

Proton-proton collisions at the LHC produce an intense collimated beam of high-energy neutrinos
in the forward direction.
%
Their recent  observation by the FASER$\nu$ and SND@LHC experiments
indicates that this hitherto discarded beam becomes now available for scientific studies.
%
Neutrino deep-inelastic scattering (DIS) is known
to provide a sensitive probe of the quark flavour separation in nucleons
and nuclei, in particular strangeness.
%
Here we assess the expected impact of DIS neutrino structure functions at the LHC
on the parton distribution functions (PDFs) of protons and heavy nuclei.
%
We consider projections for  FASER$\nu$ and SND@LHC based on the Run III luminosity
and for the  experiments hosted by the
 Forward Physics Facility (FPF) operating concurrently with the HL-LHC.
 %
 By means of both Hessian profiling within {\sc\small xFitter} and
 of the  NNPDF open-source framework,
 we demonstrate the significant PDF impact of the high-statistics FPF data
 on the region $10^{-3}\lsim x \lsim 0.7$, comparable to that covered by the
 Electron-Ion Collider (EIC) with neutral-current scattering.
%
 Our analysis highlights how exploiting the potential
 of this unique neutrino beam  effectively
extends the LHC with a ``Neutrino-Ion Collider''.

@@

% Analysis settings, theory calculations, xfitter vs NNPDFs, yadism/eko/pineappl
% Fitting vs profiling
\input{sec-analysis}

@@

% REsults for the nuclear PDFs, using NNPDF and EPPS21/xfitter
\input{sec-nuclearPDFs}

@@

%\section{Description of the $\nu$FPF codes}

%The part that computes the differential cross sections is taken care by the python
%package $\nu$FPF. By default, it computes the HERA cross section defined as
%\begin{equation}
%    \frac{d^2\tilde{\sigma}^{A}}{dxdy} \lp x,Q^2,y \rp =  \frac{1}{2}\lc (1-y)F^{\nu A}_2(x,Q^2) + y^2xF^{\nu A}_1(x,Q^2)
%    + (-1)^\ell  y\lp 1-\frac{y}{2}\rp xF^{\nu A}_3(x,Q^2)\rc ,
%\end{equation}
%where $\ell = 0$ for leptons and $\ell = 1$ for anti-leptons. Thus, in order to compare with 
%Eq.~\ref{eq:neutrino_DIS_xsec} one needs to multiply the above equation with $G_F^2s/2 \pi (1 + Q^2/m^2_W)^2$.

% Bibliography
\bibliographystyle{utphys}
\bibliography{FPF-WG1}

>>>>

Proton-proton collisions at the LHC produce an intense collimated beam of high-energy (TeV) neutrinos
in the forward direction.
%
The recent  observation of LHC neutrinos by the FASER$\nu$ and SND@LHC experiments
indicates that this hitherto ignored beam becomes available for scientific investigations.
%
Neutrino deep-inelastic scattering (DIS) is known
to provide a sensitive probe of the quark flavour separation in nucleons
and nuclei.
%
Here we quantify the projected impact of DIS neutrino structure functions at the LHC
on the parton distribution functions (PDFs) of protons and heavy nuclei.
%
We generate differential structure function DIS pseudo-data 
for  FASER$\nu$ and SND@LHC based on the Run III luminosity,
as well as for the FASER$\nu$2, AdvSND, and FLArE experiments
to be  hosted at the proposed
 Forward Physics Facility (FPF) operating concurrently with the High Luminosity LHC.
 %
 By using both the Hessian profiling of PDF4LHC21 with {\sc\small xFitter} and
 the  NNPDF open-source framework,
 we highlight the impact on the proton and nuclear PDFs of the FPF
 experiments in a kinematic region in $x$ and $Q^2$ which is comparable to that
 to be covered at the upcoming
 Electron-Ion Collider (EIC).
 %
 This sensitivity is found to be the largest for  strangeness as well as for
 the up and down valence quark PDFs.
%
 Our analysis demonstrates how exploiting the potential
 of this unique LHC neutrino beam  effectively
extends the CERN infrastructure with a ``Neutrino-Ion Collider''.

@@

@@

@@

% Appendices
\appendix

% Impact of FASERnu
\input{app-faser.tex}

% Impact in nuclear PDFs
\input{app-nuclearPDFs.tex}

\bibliographystyle{utphys}
\bibliography{FPF-WG1}
